---
title: "assignment2"
author: "AJ Fowler"
date: "1/27/2020"
output: 
  md_document:
    variant: markdown_github
---
```{r setup, include=FALSE, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)

c("ggplot2",
  "tibble",
  "tidyr",
  "readr",    
  "purrr",
  "devtools",
  "dplyr",
  "ballr",
  "stringr",
  "forcats",
  "gapminder"      
  ) -> package_names  
for(package_name in package_names) {
  if(!is.element(package_name, installed.packages()[,1])) {
     install.packages(package_name,
                      repos = "http://cran.mtu.edu/")
  }
  library(package_name, character.only=TRUE,
          quietly=TRUE,verbose=FALSE)
}

rm(list=c("package_name", "package_names")) 

options(show.signif.stars = FALSE)  
```


How are the best guards in the NBA scoring in todays NBA?

I pulled data from basketball references with the ballR package. I used data from 2019 and filtered the data to get the top 20 scoring guards in the NBA. 
```{r data wrangling}
sznstats_df <- NBAPerGameStatistics(season = 2019)

sznstats_df%>%
 filter(pos %in% c("SG", "PG")) %>%
 top_n(n = 20, pts) %>% 
distinct() -> top20guards_df
```

```{r }
ggplot(data = top20guards_df, aes(x = pts, y = player, colour = x3pa, size = fta))+
  geom_point() +
  ggtitle("Top 20 Scoring Guards", subtitle = " Points Per Game Compared by 3 Point Attempts and Freethrow Attempts")


```






After you have constructed the visualization, write a caption and a paragraph describing the visualization, and how it answers the question you posed. Think of the figure, the caption, and the text as material you might include in a research pape





